---
title: "Final Thesis Project Code"
author: "Ngoc Yen"
date: "2025-06-25"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: readable
    highlight: tango
    df_print: kable
    css: style.css
  pdf_document:
    toc: true
    toc_depth: '3'
---


## R Markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
knitr::opts_chunk$set(
  fig.width = 24,      # Figure width
  fig.height = 16,     # Figure height
  echo = TRUE,
  warning = FALSE,     # Suppress warnings in output
  message = FALSE      # Suppress messages in output
)
```
```{r}
# Set default CRAN mirror (fix contrib.url error)
options(repos = c(CRAN = "https://cran.rstudio.com"))
```

```{r}

install.packages("readxl", dependencies = TRUE)
install.packages("dplyr", dependencies = TRUE)
install.packages("Benchmarking", dependencies = TRUE)
install.packages("truncreg",dependencies = TRUE )
install.packages("cellranger", dependencies = TRUE)
install.packages("ggplot2", dependencies = TRUE)
install.packages("tidyr", dependencies = TRUE)
install.packages("AER", dependencies = TRUE)
install.packages("stargazer", dependencies = TRUE)
install.packages("psych", dependencies = TRUE)
install.packages("knitr", dependencies = TRUE)
install.packages("gtable", dependencies = TRUE)
```
```{r}
 install.packages("knitr", dependencies = TRUE)
```
```{r}
install.packages("psych", dependencies = TRUE)
```



```{r}
library(readxl)
library(Benchmarking)
library(dplyr)
library(cellranger)
library(ggplot2)
library(tidyr) 
library(psych) 
library(knitr)
library(AER)
library(stargazer)
library(truncreg)
library(gridExtra)
library(texreg)
library(xfun)
```





# Phase 1: Data Envelopment Analysis (DEA)
This phase calculates Overall Technical Efficiency (OTE) using the CRS model, Pure Technical Efficiency (PTE) using the VRS model, and Scale Efficiency (SE).

#1.1 Data Import and Initial Cleaning for DEA

```{r}
dea_raw <- read_excel("D:/dea/deaxl/DEA.xlsx", sheet = "Tổng hợp", range = cell_limits(c(1, 1), c(211, 11)))

cat("--- Raw DEA Data after Import (dea_raw) ---\n")
head(dea_raw, n = 10)
```

```{r}
cat("--- Raw DEA Data after Import (dea_raw) ---\n")
```
#1.2 Check Dimensions and Column Names of Raw Data

```{r}
print(dim(dea_raw))
```

```{r}
head(dea_raw, n = 10)
```
```{r}
cat("\n--- Column Names in dea_raw ---\n")
print(colnames(dea_raw))
```
#1.3 Clean and Transform DEA Data 

```{r}
# Clean and transform variables for DEA analysis
# Filter out rows with NA values in critical input/output columns and the firm type column.
# Convert relevant columns to numeric type.
# Create a clear 'Firm_Type' column based on 'Life_Insurance=1'.
dea_clean <- dea_raw %>%
 filter(!is.na(`Financial Investment Income`),
         !is.na(`Benefits/ losses incurred`),
         !is.na(`Total Operating Exp`),
         !is.na(`Total Debt`),
         !is.na(`Total Equity`),
         !is.na(`Dummy (Life_Insurance=1)`)) %>%
  mutate(across(c(`Financial Investment Income`, `Benefits/ losses incurred`, `Total Operating Exp`, `Total Debt`, `Total Equity`, `Dummy (Life_Insurance=1)`), as.numeric)) %>% 
 mutate(Firm_Type = ifelse(`Dummy (Life_Insurance=1)` == 1, "Life", "Non-Life")) 
cat("\n--- Cleaned DEA Data with Firm Type (dea_clean) ---\n")
head(dea_clean)
str(dea_clean) 

```



# 1.4 Define Inputs and Outputs for DEA
```{r}
# Split data into Life and Non-Life firms for separate DEA analysis
dea_life_data <- dea_clean %>% filter(Firm_Type == "Life")
dea_nonlife_data <- dea_clean %>% filter(Firm_Type == "Non-Life")

cat("\n--- Dimensions of Life Insurance Data for DEA ---\n")
print(dim(dea_life_data))
cat("\n--- Dimensions of Non-Life Insurance Data for DEA ---\n")
print(dim(dea_nonlife_data))

# Define inputs and outputs for Life Insurance Firms
inputs_life <- as.matrix(dea_life_data[, c("Total Operating Exp", "Total Debt", "Total Equity")])
outputs_life <- as.matrix(dea_life_data[, c("Financial Investment Income", "Benefits/ losses incurred")])

# Define inputs and outputs for Non-Life Insurance Firms
inputs_nonlife <- as.matrix(dea_nonlife_data[, c("Total Operating Exp", "Total Debt", "Total Equity")])
outputs_nonlife <- as.matrix(dea_nonlife_data[, c("Financial Investment Income", "Benefits/ losses incurred")])

cat("\n--- Dimensions of Inputs and Outputs Matrices for Life Firms ---\n")
print(dim(inputs_life))
print(dim(outputs_life))
cat("\n--- Dimensions of Inputs and Outputs Matrices for Non-Life Firms ---\n")
print(dim(inputs_nonlife))
print(dim(outputs_nonlife))

```


#1.5  Run DEA Models: CRS, VRS, and Calculate Scale Efficiency
```{r}
# --- For Life Insurance Firms ---
life_eff_scores <- data.frame(Firm = dea_life_data$Firm, Year = dea_life_data$Year, Firm_Type = "Life")
if (nrow(dea_life_data) > 0 && ncol(inputs_life) > 0 && ncol(outputs_life) > 0 && sum(rowSums(inputs_life) > 0) > 0 && sum(rowSums(outputs_life) > 0) > 0) {
  dea_result_life_crs <- dea(inputs_life, outputs_life, RTS = "crs", ORIENTATION = "in")
  dea_result_life_vrs <- dea(inputs_life, outputs_life, RTS = "vrs", ORIENTATION = "in")
  life_eff_scores$OTE <- dea_result_life_crs$eff
  life_eff_scores$PTE <- dea_result_life_vrs$eff
  life_eff_scores$SE <- life_eff_scores$OTE / life_eff_scores$PTE
  cat("\n--- Summary of DEA Results (Life Firms - CRS Model) ---\n")
  summary(dea_result_life_crs)
  cat("\n--- Summary of DEA Results (Life Firms - VRS Model) ---\n")
  summary(dea_result_life_vrs)
} else {
  cat("\nWarning: Insufficient data or invalid inputs/outputs for DEA for Life Insurance Firms. Efficiency scores will be NA.\n")
  life_eff_scores$OTE <- NA
  life_eff_scores$PTE <- NA
  life_eff_scores$SE <- NA
}
```


```{r}
# --- For Non-Life Insurance Firms ---
nonlife_eff_scores <- data.frame(Firm = dea_nonlife_data$Firm, Year = dea_nonlife_data$Year, Firm_Type = "Non-Life")
if (nrow(dea_nonlife_data) > 0 && ncol(inputs_nonlife) > 0 && ncol(outputs_nonlife) > 0 && sum(rowSums(inputs_nonlife) > 0) > 0 && sum(rowSums(outputs_nonlife) > 0) > 0) {
  dea_result_nonlife_crs <- dea(inputs_nonlife, outputs_nonlife, RTS = "crs", ORIENTATION = "in")
  dea_result_nonlife_vrs <- dea(inputs_nonlife, outputs_nonlife, RTS = "vrs", ORIENTATION = "in")
  nonlife_eff_scores$OTE <- dea_result_nonlife_crs$eff
  nonlife_eff_scores$PTE <- dea_result_nonlife_vrs$eff
  nonlife_eff_scores$SE <- nonlife_eff_scores$OTE / nonlife_eff_scores$PTE
  cat("\n--- Summary of DEA Results (Non-Life Firms - CRS Model) ---\n")
  summary(dea_result_nonlife_crs)
  cat("\n--- Summary of DEA Results (Non-Life Firms - VRS Model) ---\n")
  summary(dea_result_nonlife_vrs)
} else {
  cat("\nWarning: Insufficient data or invalid inputs/outputs for DEA for Non-Life Insurance Firms. Efficiency scores will be NA.\n")
  nonlife_eff_scores$OTE <- NA
  nonlife_eff_scores$PTE <- NA
  nonlife_eff_scores$SE <- NA
}
```
#1.6 Combine Efficiency Scores (Life + Non-Life)

```{r}
# Combine efficiency scores from both groups
all_eff_scores_detailed <- bind_rows(life_eff_scores, nonlife_eff_scores)
```

```{r}
cat("\n--- All Efficiency Scores (Combined, Group-Specific DEA) ---\n")
head(all_eff_scores_detailed)
str(all_eff_scores_detailed)
```

#1.7 Filter for Valid Efficiency Scores
```{r}
plot_data_all_eff <- all_eff_scores_detailed %>%
  filter(!is.na(OTE) & OTE >= 0 & OTE <= 1,
         !is.na(PTE) & PTE >= 0 & PTE <= 1,
         !is.na(SE) & SE >= 0 & SE <= 1)
```


```{r}
# Non-Life PTE Distribution (from VRS)
nonlife_pte <- plot_data_all_eff %>%
  filter(Firm_Type == "Non-Life") %>%
  mutate(PTE_Group = cut(PTE,
                         breaks = c(0.6, 0.7, 0.8, 0.9, 0.9999, 1.01),
                         labels = c("0.60 ≤ E < 0.70",
                                    "0.70 ≤ E < 0.80",
                                    "0.80 ≤ E < 0.90",
                                    "0.90 ≤ E < 1.00",
                                    "E = 1.00"),
                         right = FALSE))

table_pte_nonlife <- nonlife_pte %>%
  group_by(PTE_Group) %>%
  summarise(Count = n()) %>%
  mutate(Percent = round(Count / sum(Count) * 100, 1))

kable(table_pte_nonlife,
      caption = "Table 4.6: Distribution of PTE Scores for Non-Life Insurance Firms",
      col.names = c("Efficiency Interval", "Number of Firms", "Percentage (%)"))
```



```{r}
# Life PTE Distribution (from VRS)
life_pte <- plot_data_all_eff %>%
  filter(Firm_Type == "Life") %>%
  mutate(PTE_Group = cut(PTE,
                         breaks = c(0.6, 0.7, 0.8, 0.9, 0.9999, 1.01),
                         labels = c("0.60 ≤ E < 0.70",
                                    "0.70 ≤ E < 0.80",
                                    "0.80 ≤ E < 0.90",
                                    "0.90 ≤ E < 1.00",
                                    "E = 1.00"),
                         right = FALSE))

table_pte_life <- life_pte %>%
  group_by(PTE_Group) %>%
  summarise(Count = n()) %>%
  mutate(Percent = round(Count / sum(Count) * 100, 1))

kable(table_pte_life,
      caption = "Table 4.5: Distribution of PTE Scores for Life Insurance Firms",
      col.names = c("Efficiency Interval", "Number of Firms", "Percentage (%)"))
```

```{r}
library(ggplot2)
library(dplyr)


life_pte <- data.frame(
  Interval = c("0.60–0.70", "0.70–0.80", "0.80–0.90", "0.90–1.00", "1.00"),
  Count = c(4, 16, 20, 29, 26)
)
nonlife_pte <- data.frame(
  Interval = c("0.60–0.70", "0.70–0.80", "0.80–0.90", "0.90–1.00", "1.00"),
  Count = c(4, 8, 38, 32, 30)
)
pte_data <- bind_rows(
  mutate(life_pte, Type = "Life"),
  mutate(nonlife_pte, Type = "Non-Life")
)


ggplot(pte_data, aes(x = Interval, y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(title = "Distribution of Pure Technical Efficiency (PTE)",
       x = "Efficiency Interval",
       y = "Number of Firms") +
  scale_fill_manual(values = c("Life" = "#4C6EF5", "Non-Life" = "#ADB5BD")) +
  theme_minimal(base_size = 14)

```


```{r}
#choose variables input/output
dea_vars <- dea_clean %>%
  select(`Total Operating Exp`, `Total Debt`, `Total Equity`,
         `Financial Investment Income`, `Benefits/ losses incurred`) / 1e9


dea_desc_stats <- describe(dea_vars)


dea_table <- round(dea_desc_stats[, c("mean", "sd", "min", "max")], 2)


rownames(dea_table) <- c("Total Operating Expenses",
                         "Total Debt",
                         "Total Equity",
                         "Financial Inv. Income",
                         "Benefits/Losses Incurred")


kable(dea_table,
      caption = "Table 4.1: Descriptive Statistics for DEA Inputs and Outputs (Unit: Billion VND)",
      digits = 2,
      format.args = list(big.mark = ",")) 
```

```{r}
names(dea_clean)
```

```{r}
dea_clean_billion <- dea_clean %>%
  mutate(
    `Total Operating Exp` = `Total Operating Exp` / 1e9,
    `Total Debt` = `Total Debt` / 1e9,
    `Total Equity` = `Total Equity` / 1e9,
    `Financial Investment Income` = `Financial Investment Income` / 1e9,
    `Benefits/ losses incurred` = `Benefits/ losses incurred` / 1e9
  )
```


```{r}
dea_long <- dea_clean_billion %>%
  select(`Total Operating Exp`, `Total Debt`, `Total Equity`,
         `Financial Investment Income`, `Benefits/ losses incurred`) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value")

ggplot(dea_long, aes(x = Value)) +
  geom_histogram(fill = "white", color = "black", bins = 30) +
  facet_wrap(~ Variable, scales = "free", ncol = 2) +
  scale_x_log10() +  # ✨ chuyển trục X sang log-scale
  theme_bw(base_size = 12) +
  labs(
    title = "Histogram of DEA Inputs and Outputs (Log Scale, Unit: Billion VND)",
    x = "Value (Log scale, Billion VND)", y = "Frequency"
  )
```

```{r}
# Average DEA Inputs and Outputs by Year
dea_by_year <- dea_clean %>%
  group_by(Year) %>%
  summarise(
    `Total Operating Expenses` = mean(`Total Operating Exp`, na.rm = TRUE) / 1e9,
    `Total Debt` = mean(`Total Debt`, na.rm = TRUE) / 1e9,
    `Total Equity` = mean(`Total Equity`, na.rm = TRUE) / 1e9,
    `Financial Investment Income` = mean(`Financial Investment Income`, na.rm = TRUE) / 1e9,
    `Benefits/Losses Incurred` = mean(`Benefits/ losses incurred`, na.rm = TRUE) / 1e9
  ) %>%
  pivot_longer(cols = -Year, names_to = "Variable", values_to = "Avg_Value")


ggplot(dea_by_year, aes(x = Year, y = Avg_Value, group = Variable)) +
  geom_line(color = "black", size = 1) +
  geom_point(color = "black", size = 2) +
  facet_wrap(~ Variable, scales = "free_y", ncol = 2) +
  theme_bw(base_size = 13) +
  labs(
    title = "Average DEA Inputs and Outputs by Year (Unit: Billion VND)",
    x = "Year",
    y = "Average Value"
  ) +
  theme(
    strip.background = element_rect(fill = "gray90", color = "black"),
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14)
  )
```


#1.9 Save All Efficiency Scores

```{r}
# Save the detailed efficiency scores to a CSV file
write.csv(all_eff_scores_detailed, "D:/dea/deaxl/all_efficiency_scores_detailed.csv", row.names = FALSE)

cat("\n--- All Efficiency Scores with Firm Type Saved to all_efficiency_scores_detailed.csv ---\n")
head(all_eff_scores_detailed, n=10)

```
```{r}
table_avg_eff_firmtype <- plot_data_all_eff %>%
  group_by(Firm_Type) %>%
  summarise(
    Avg_OTE = round(mean(OTE, na.rm = TRUE), 3),
    Avg_PTE = round(mean(PTE, na.rm = TRUE), 3),
    Avg_SE = round(mean(SE, na.rm = TRUE), 3)
  )

table_avg_eff_firmtype
```



# Table Average by Year 

```{r}
table_avg_eff_year <- plot_data_all_eff %>%
  group_by(Year) %>%
  summarise(
    Avg_OTE = round(mean(OTE, na.rm = TRUE), 3),
    Avg_PTE = round(mean(PTE, na.rm = TRUE), 3),
    Avg_SE = round(mean(SE, na.rm = TRUE), 3)
  )

table_avg_eff_year
```



```{r}
 #Calculate descriptive statistics for DEA indices
dea_stats <- all_eff_scores_detailed %>%
  select(OTE, PTE, SE) %>%
  summarise(
    OTE_Mean = mean(OTE, na.rm = TRUE),
    OTE_SD   = sd(OTE, na.rm = TRUE),
    OTE_Min  = min(OTE, na.rm = TRUE),
    OTE_Max  = max(OTE, na.rm = TRUE),
    
    PTE_Mean = mean(PTE, na.rm = TRUE),
    PTE_SD   = sd(PTE, na.rm = TRUE),
    PTE_Min  = min(PTE, na.rm = TRUE),
    PTE_Max  = max(PTE, na.rm = TRUE),
    
    SE_Mean = mean(SE, na.rm = TRUE),
    SE_SD   = sd(SE, na.rm = TRUE),
    SE_Min  = min(SE, na.rm = TRUE),
    SE_Max  = max(SE, na.rm = TRUE)
  )

dea_summary <- tibble::tibble(
  `Score Type` = c("OTE", "PTE", "SE"),
  Mean     = c(dea_stats$OTE_Mean, dea_stats$PTE_Mean, dea_stats$SE_Mean),
  `Std. Dev.` = c(dea_stats$OTE_SD, dea_stats$PTE_SD, dea_stats$SE_SD),
  Min      = c(dea_stats$OTE_Min, dea_stats$PTE_Min, dea_stats$SE_Min),
  Max      = c(dea_stats$OTE_Max, dea_stats$PTE_Max, dea_stats$SE_Max)
)

dea_summary[, 2:5] <- round(dea_summary[, 2:5], 2)

dea_summary
```



```{r}
# Average DEA Efficiency Scores by Year – Life Insurance Firms
eff_by_year_life <- all_eff_scores_detailed %>%
  filter(Firm_Type == "Life") %>%
  group_by(Year) %>%
  summarise(
    Avg_OTE = mean(OTE, na.rm = TRUE),
    Avg_PTE = mean(PTE, na.rm = TRUE),
    Avg_SE = mean(SE, na.rm = TRUE)
  ) %>%
  pivot_longer(cols = starts_with("Avg_"), names_to = "Score_Type", values_to = "Value")

ggplot(eff_by_year_life, aes(x = Year, y = Value, color = Score_Type, group = Score_Type)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  scale_color_manual(
    values = c("Avg_OTE" = "gray30",   
               "Avg_PTE" = "gray50",    
               "Avg_SE"  = "gray70"),   
    labels = c("OTE", "PTE", "SE")
  ) +
  labs(
    title = "Figure 4.5: Average DEA Efficiency Scores by Year – Life Insurance Firms",
    x = "Year", y = "Average Score", color = "Score Type"
  ) +
  theme_bw(base_size = 13) +
  ylim(0.6, 1.0)
```
```{r}
# Average DEA Efficiency Scores by Year – Non-Life Insurance Firms
eff_by_year_nonlife <- all_eff_scores_detailed %>%
  filter(Firm_Type == "Non-Life") %>%
  group_by(Year) %>%
  summarise(
    Avg_OTE = mean(OTE, na.rm = TRUE),
    Avg_PTE = mean(PTE, na.rm = TRUE),
    Avg_SE = mean(SE, na.rm = TRUE)
  ) %>%
  pivot_longer(cols = starts_with("Avg_"), names_to = "Score_Type", values_to = "Value")


ggplot(eff_by_year_nonlife, aes(x = Year, y = Value, color = Score_Type, group = Score_Type)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  scale_color_manual(
    values = c("Avg_OTE" = "black",     
               "Avg_PTE" = "dimgray",   
               "Avg_SE"  = "steelblue4"), 
    labels = c("OTE", "PTE", "SE")
  ) +
  labs(
    title = "Figure 4.6: Average DEA Efficiency Scores by Year – Non-Life Insurance Firms",
    x = "Year", y = "Average Score", color = "Score Type"
  ) +
  theme_bw(base_size = 13) +
  ylim(0.6, 1.0)
```

```{r}
# Convert to long form for easy histogram drawing
eff_hist_data <- all_eff_scores_detailed %>%
  pivot_longer(cols = c(OTE, PTE, SE), 
               names_to = "Efficiency_Type", 
               values_to = "Efficiency_Score") %>%
  filter(!is.na(Efficiency_Score)) 
```


```{r}
# Histogram for Life Firms
eff_hist_data %>%
  filter(Firm_Type == "Life") %>%
  ggplot(aes(x = Efficiency_Score)) +
  geom_histogram(bins = 20, fill = "#4D4D4D", color = "white", alpha = 0.8) +
  facet_wrap(~ Efficiency_Type, scales = "free_y") +
  theme_bw(base_size = 13) +
  labs(
    title = "Figure 4.7: Histogram of DEA Efficiency Scores – Life Insurance Firms",
    x = "Efficiency Score",
    y = "Frequency"
  ) +
  theme(strip.background = element_rect(fill = "gray90", color = NA),
        strip.text = element_text(face = "bold"),
        plot.title = element_text(hjust = 0.5, face = "bold"))
```

```{r}
# Histogram for Non-Life Firms
eff_hist_data %>%
  filter(Firm_Type == "Non-Life") %>%
  ggplot(aes(x = Efficiency_Score)) +
  geom_histogram(bins = 20, fill = "#6C7A89", color = "white", alpha = 0.8) +
  facet_wrap(~ Efficiency_Type, scales = "free_y") +
  theme_bw(base_size = 13) +
  labs(
    title = "Figure 4.8: Histogram of DEA Efficiency Scores – Non-Life Insurance Firms",
    x = "Efficiency Score",
    y = "Frequency"
  ) +
  theme(strip.background = element_rect(fill = "gray90", color = NA),
        strip.text = element_text(face = "bold"),
        plot.title = element_text(hjust = 0.5, face = "bold"))
```



# Phase 2: Determinants Analysis using Truncated Regression
This stage combines the DEA efficiency scores with firm-specific and macroeconomic determinants and performs truncated regression analysis. The use of a truncated regression model is appropriate given the bounded nature of DEA efficiency scores between 0 and 1.


#2.1 Data Import and Initial Cleaning 
```{r}
reg_raw <- read_excel("D:/data/regress/Regression.xlsx", sheet = "Sheet1")
```


```{r}
cat("--- Raw Regression Data (reg_raw) ---\n")
head(reg_raw, n=10)
str(reg_raw)
```
#2.2 Clean and Transform Regression Variables

```{r}
# Clean and prepare regression variables
reg_clean <- reg_raw %>%
  filter(!is.na(LEV), !is.na(GWP), !is.na(SIZE), !is.na(`Interest Rate`), !is.na(`%Inflation`)) %>%
  mutate(
    across(c(LEV, GWP, SIZE, AGE, LIFEDUM, `Interest Rate`, `%Inflation`), as.numeric),
    
    Size_log = log(SIZE) 
  ) %>%
  rename(Leverage = LEV,
         Gross_Written_Premium = GWP,
         Interest_Rate = `Interest Rate`, # Macroeconomic variable
         Inflation_Rate = `%Inflation`) %>% # Macroeconomic variable
  group_by(Firm) %>%
  mutate(Growth = (Gross_Written_Premium - lag(Gross_Written_Premium)) / lag(Gross_Written_Premium)) %>%
  ungroup() %>%
  filter(!is.na(Growth))
```

```{r}
eff_data <- read.csv("D:/dea/deaxl/all_efficiency_scores_detailed.csv")

```


#2.3 Merge Regression Data with DEA Efficiency Scores


```{r}

reg_merged <- left_join(reg_clean, eff_data, by = c("Firm", "Year"))

reg_merged <- reg_merged %>%
  filter(!is.na(OTE), 
         !is.na(Leverage), 
         !is.na(Gross_Written_Premium),
         !is.na(Size_log),
         !is.na(Growth),
         !is.na(Interest_Rate),
         !is.na(Inflation_Rate),
         !is.na(AGE),
         !is.na(Firm_Type)) # Crucial for splitting analysis

cat("\n--- Merged Data for Regression (reg_merged) ---\n")
head(reg_merged)
str(reg_merged)
summary(reg_merged$OTE)

```
#2.4 Descriptive Statistics of Regression Variables
```{r}

reg_vars <- reg_merged %>%
  select(OTE, Size_log, Leverage, Growth, Interest_Rate, Inflation_Rate, AGE)

desc_stats <- describe(reg_vars)
summary_table <- round(desc_stats[, c("mean", "sd", "min", "max")], 2)

rownames(summary_table) <- c("OTE", "Size_log", "Leverage", "Growth", 
                             "Interest_Rate", "Inflation_Rate", "AGE")

kable(summary_table,
      caption = "Table 4.2: Descriptive Statistics for Truncated Regression",
      col.names = c("Mean", "Std. Dev.", "Min", "Max"))
```
#2.5 Subset Data by Firm Type (Life vs Non-Life)

```{r}
life_data <- reg_merged %>% filter(Firm_Type == "Life")
nonlife_data <- reg_merged %>% filter(Firm_Type == "Non-Life")
```


```{r}
cat("Life Insurance Firms:", nrow(life_data), "\n")
cat("Non-Life Insurance Firms:", nrow(nonlife_data), "\n")
```
#2.6 Visualize Regression Variables (Histograms)

```{r}
library(gridExtra)


reg_vars_long <- reg_vars %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value")

ggplot(reg_vars_long, aes(x = Value)) +
  geom_histogram(color = "black", fill = "white", bins = 20) +
  facet_wrap(~ Variable, scales = "free", ncol = 3) +
  labs(title = "Histogram of Truncated Regression Variables", x = "Value") +
  theme_minimal()

```
```{r}
reg_vars_long <- reg_merged %>%
  select(Year, OTE, Size_log, Leverage, Growth, Interest_Rate, Inflation_Rate, AGE) %>%
  pivot_longer(cols = -Year, names_to = "Variable", values_to = "Value")

reg_data_yearly <- reg_vars_long %>%
  group_by(Year, Variable) %>%
  summarise(Average = mean(Value, na.rm = TRUE), .groups = "drop")

```


```{r}
reg_data_yearly$Variable <- dplyr::recode(reg_data_yearly$Variable,
                                   "OTE" = "Technical Efficiency (OTE)",
                                   "Size_log" = "Firm Size (log)",
                                   "Leverage" = "Leverage Ratio",
                                   "Growth" = "Growth Rate",
                                   "Interest_Rate" = "Interest Rate",
                                   "Inflation_Rate" = "Inflation Rate",
                                   "AGE" = "Firm Age")

reg_data_yearly$Variable <- case_when(
  reg_data_yearly$Variable == "OTE" ~ "Technical Efficiency (OTE)",
  reg_data_yearly$Variable == "Size_log" ~ "Firm Size (log)",
  reg_data_yearly$Variable == "Leverage" ~ "Leverage Ratio",
  reg_data_yearly$Variable == "Growth" ~ "Growth Rate",
  reg_data_yearly$Variable == "Interest_Rate" ~ "Interest Rate",
  reg_data_yearly$Variable == "Inflation_Rate" ~ "Inflation Rate",
  reg_data_yearly$Variable == "AGE" ~ "Firm Age",
  TRUE ~ reg_data_yearly$Variable
)

ggplot(reg_data_yearly, aes(x = Year, y = Average)) +
  geom_line(color = "black") +
  geom_point(color = "black") +
  facet_wrap(~ Variable, scales = "free_y", ncol = 2) +
  labs(title = "Figure 4.4 Average Values of Truncated Regression Variables by Year",
       x = "Year", y = "Average Value") +
  theme_minimal(base_size = 12) +
  theme(strip.background = element_rect(fill = "gray90"),
        strip.text = element_text(face = "bold"),
        plot.title = element_text(hjust = 0.5, face = "bold"))
```

#2.7 Run Truncated Regression Models:

```{r}
# Truncated Regression For All Insurance Firm 
trunc_all <- truncreg(OTE ~ Leverage + Size_log + AGE + Growth + Interest_Rate + Inflation_Rate,
                      data = reg_merged,
                      lower = 0, # Giới hạn dưới của biến phụ thuộc
                      upper = 1) # Giới hạn trên của biến phụ thuộc

screenreg(trunc_all,
          custom.coef.names = c("(Intercept)", "Leverage", "Log of Size", "Firm Age", "Growth", "Interest Rate", "Inflation Rate", "Sigma"), # Đã thêm "Sigma"
          custom.model.names = "All Insurance Firms",
          caption = "Table 4.8: Truncated Regression Results for All Insurance Firms",
          digits = 3)
```



```{r}
# Truncated Regression For Life Insurance Firms 
trunc_life <- truncreg(OTE ~ Leverage + Size_log + AGE + Growth + Interest_Rate + Inflation_Rate,
                       data = life_data,
                       lower = 0, 
                       upper = 1) 
summary(trunc_life)
```


```{r}
# Truncated Regression For Non-Life Insurance Firms 
trunc_nonlife <- truncreg(OTE ~ Leverage + Size_log + AGE + Growth + Interest_Rate + Inflation_Rate,
                          data = nonlife_data,
                          lower = 0, 
                          upper = 1) 
summary(trunc_nonlife)
```
#2.8 Summary Table 


```{r}
screenreg(list("Life Insurance" = trunc_life, "Non-Life Insurance" = trunc_nonlife),
          custom.model.names = c("Life Insurance", "Non-Life Insurance"),
          digits = 3,
          caption = "Truncated Regression Results for Life and Non-Life Insurance Firms")


```




















